\paperTitle

### 2014-05-17 doc/icml2014/discussion.tex
Ran through aspell

% Correlation structure
Other authors, e.g \citet{anandkumar12lda, anandkumar2013linear,
  halpern13noisyor}, learn parameters for models outside this
  family, but they do so with some knowledge of the correlation structure
  between hidden variables. 
In a pre-processing step, they ``subtract'' out the correlations and
  recover a graph that is bottlenecked.
% TOO BOLD
%Thus, while \propertyref{bottleneck} is much stronger than
%  \propertyref{exclusive-views}, we expect that without any knowledge of
%  the correlation between variables, \propertyref{bottleneck} is
%  necessary for identifiability.
%Our work uses the \TensorFactorize algorithm presented by
%  \citet{anandkumar13tensor}, first
%  studied the consistent parameter estimation algorithm for the
%  three-view mixture model.
%
%\todo{What about Mossel and Roch?}
For example,
\citet{anandkumar12lda} are able to recover parameters for correlated
  discrete mixtures, e.g. latent Dirichlet allocation; their approach
  follows that of the three-view mixture model, with a pre-processing step
  that subtracts the correlation between the views.
\citet{anandkumar2013linear} study a special family of Bayesian networks
  in which the observed variables are linearly related to a sparse set of
  hidden variables. Once again, the key step is to identify the
  correlations between observed variables and exclude them from the views.
\citet{halpern13noisyor} propose an algorithm to recover factors for
  a more densely connected bipartite noisy-or network; they also use
  bottlenecks to learn parameters, but exploit properties of the model
  to negate correlations from learned edges, allowing for more
  bottlenecks to be discovered. 
Our work makes a different tradeoff: we do not assume any special correlation structure,
but do rely on every hidden variable having an exclusive view so that we can
learn the underlying structure.

>>>>

% Correlation structure
Other authors, e.g \citet{anandkumar12lda, anandkumar2013linear,
  halpern13noisyor}, learn parameters for models outside this
  family, but they do so with some knowledge of the correlation structure
  between hidden variables. 
In a preprocessing step, they ``subtract'' out the correlations and
  recover a graph that is bottlenecked.
% TOO BOLD
%Thus, while \propertyref{bottleneck} is much stronger than
%  \propertyref{exclusive-views}, we expect that without any knowledge of
%  the correlation between variables, \propertyref{bottleneck} is
%  necessary for identifiability.
%Our work uses the \TensorFactorize algorithm presented by
%  \citet{anandkumar13tensor}, first
%  studied the consistent parameter estimation algorithm for the
%  three-view mixture model.
%
%\todo{What about Mossel and Roch?}
For example,
\citet{anandkumar12lda} are able to recover parameters for correlated
  discrete mixtures, e.g. latent Dirichlet allocation; their approach
  follows that of the three-view mixture model, with a preprocessing step
  that subtracts the correlation between the views.
\citet{anandkumar2013linear} study a special family of Bayesian networks
  in which the observed variables are linearly related to a sparse set of
  hidden variables. Once again, the key step is to identify the
  correlations between observed variables and exclude them from the views.
\citet{halpern13noisyor} propose an algorithm to recover factors for
  a more densely connected bipartite noisy-or network; they also use
  bottlenecks to learn parameters, but exploit properties of the model
  to negate correlations from learned edges, allowing for more
  bottlenecks to be discovered. 
Our work makes a different tradeoff: we do not assume any special correlation structure,
but do rely on every hidden variable having an exclusive view so that we can
learn the underlying structure.
